A generic and fast C++ optimization framework

### 2017-10-19 paper.tex
Step by step guide to write simple optimization function (not sure we have to do it step by step).

\begin{itemize}
  \item {\tt Evaluate()} Evaluate a function.
  \item {\tt Gradient()}: Evaluate the gradient of a function.

  \item {\tt PartialGradient()} Evaluate the partial (sparse) gradient of a
      function.

@@

For instance, the code below defines a simple sparse function, where each
dimension has a parabola with a distinct minimum.

@@

@@

  \item {\bf Else:} Conditional Gradient Descent (Frank-Wolfe algorithm)

>>>>

\begin{itemize}
  \item {\tt Evaluate()}: Evaluate a function with the given function parameter.

  \item {\tt Gradient()}: Evaluate the gradient of a function with the given
      function parameter and return the gradient.

  \item {\tt PartialGradient()}: Evaluate the partial (sparse) gradient of a
      function with the given parameter and return the partial gradient.

@@

This section details the usage of mlpack's optimization framework. In this
example, we would like to minimize a simple sparse function, where each
dimension has a parabola with a distinct minimum. In this example, we will show
how we can use mlpack’s framework for this task, and obtain the objective of the
sparse function shown below.

@@

First, we would like to define {\tt Optimize()} which takes the function we like
to optimize and the function parameters as an Armadillo dense matrix type as
input.

\begin{minted}{c++}
template<typename FunctionType, typename ParameterType>
double Optimize(DecomposableFunctionType& function, ParameterType& parameter);
\end{minted}

Now, we can use {\tt Gradient()} to write a simple stochastic gradient descent
method with a static learning rate to optimize the function parameter.

\begin{minted}{c++}
for (size_t i = 0; i < 300; ++i)
{
  const size_t functionIndex = i % 4;
  function.Gradient(parameter, functionIndex, gradient);
  parameter -= 0.1 * gradient;
}
\end{minted}

Lastly, we would like to calculate the final objective. This can be done by
iterating over the parameter space using {\tt Evaluate()}.

\begin{minted}{c++}
double objective = 0;
for (size_t i = 0; i < 4; ++i)
  objective += function.Evaluate(parameter, i);
\end{minted}

Using this code, we can compile the code, and when we run it we receive the
following output:

xxxx

This simple example, of course, does not discuss all the intricacies like a more
complex learning rate update routine, but instead presents how the optimization
framework could be used in a simple data science context. Adapting the example
to a real-life application would be more straightforward.

@@

  \item {\bf Other:} Conditional Gradient Descent (Frank-Wolfe algorithm)
